---
title: "Data Science Section 09/23/21"
author: "Dominic Valentino"
date: "9/23/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this exercise, your task is to use the list of variables to take the `messy_data` data set and clean it so that it looks like the `clean_data` data set that we used in class. If you think you've got it, you can check to see if the two data frames are equivalent by using `clean_data == my_data` (assuming you call your data frame `my_data`), which will compare the data frames entry-wise.

```{r}

library(readr)
library(dplyr)
library(tidyverse)
library(janitor)

messy_data <- read_csv("Sep23ClassData_messy.csv")

clean_data <- read_csv("Sep23ClassData_clean.csv")

new_data <- messy_data %>%
  mutate(party = case_when(pid3 == "Republican" | grepl("Republican", pid_lean) ~ "Republican",
                           pid3 == "Democrat" | grepl("Democrat", pid_lean) ~ "Democrat",
                           pid3 == "Independent" |grepl("Independent", pid_lean) ~ "Independent",
                           T ~ NA_character_)) %>%
  pivot_longer(cols = contains("Republican") ,
               names_to = "treatment",
               names_pattern = "(.*)Republican",
               values_to = "marryRepublican") %>%
  pivot_longer(cols = contains("Democrat"),
               names_to = "treatment1",
               names_pattern = "(.*)Democrat",
               values_to = "marryDemocrat")
  

```


Variable Name         | Variable Description
--------------------- | --------------------------------------
\texttt{pid3}         | Political party preference
\texttt{pid\_lean}       | If a respondent didn't identify with the Democrats or Republicans in \texttt{pid3}, this indicates to which party (or neither) they feel closer
\texttt{strongGOP}    | Indicator variable for whether the respondent identifies as a Strong Republican
\texttt{strongDEM}    | Indicator variable for whether the respondent identifies as a Strong Democrat
\texttt{strongPARTISAN}| Indicator variable for whether the respondent identifies as a strong member of either major party
\texttt{party}        | Party variable where those who lean toward either major party are counted as identifying with that party
\texttt{treatment}    | Which treatment condition the respondent was randomly assigned to
\texttt{marryDemocrat}| The respondent's answer to how happy they would be if their child married a Democrat
\texttt{marryRepublican}| The respondent's answer to how happy they would be if their child married a Republican
\texttt{inPartyHappy} | Indicator variable for whether the respondent would be happy if their child married a member of their own party
\texttt{outPartyUnhappy}| Indicator variable for whether the respondent would be unhappy if their child married a member of the other major party
\texttt{polarized}    | Indicator variable for whether the respondent was affectively polarized
